Re-finding to support a Deep Web Question Answering System

### 2010-03-04 trunk/paper/semsearch10/content/ontological_realms.tex
Added a citation for DBpedia to the section ontological realms

\section{Representing and Ontological Realms}
\subsection{Category Heterarchy} 
% Author: Clint 
Two types of ontologies are used by our system:
\begin{enumerate}
\item Realm ontologies, comprising a heterarchy of categories that
  characterize terms that can appear in queries.
\item SSQ ontologies, used to describe the form of particular
  realm-specific queries.
\end{enumerate}
For any particular ontological realm, the number of potential
terms and their associated categories can be quite large.
Construction of a realm ontology and the terms associated
with its categories would be an extremely laborious task
for any non-trivial realm. The realm of automobiles (which
we use for illustration in this paper) contains, for example,
over XXXX categories and XXXX terms. We were unable to find
an appropriate ontology for this realm, so we constructed it
using categories from the DBPedia [!!!! citation needed].
The primary benefit of using the DBPedia for this purpose is
that not only does it supply a categorical heterarchy, but it
also links to wikipedia documents which provides us with a large
realm-specific document corpus.

To support our process, we map DBPedia categories into classes in our
realm ontology with the superclass/subclass relationships built using
DBPedia properties broader/narrower.  By using OWL, we can exploit the
OWL API for matching SSQ ontologies that reference these realm
ontologies.

%-------------------------------------------------------------------------------

@@

The subcategories of the category Automobiles (… Driving, Traffic Law,
Automobiles by Decade, Auto Racing…) can be seen as grabbing
information specific to the category. The supercategories (Road
Vehicles) place the category in a higher perspective, abstractly
describing basketball as a concept. The spousal categories
(...Motorsport, Individual Sport...) are an abstract description of
the subcategories.

Clustering the categories alone does not guarantee adequate corpus
creation. Since the above model relies on the subcategories to
describe specifics of a given category, the ideal situation would be
that the subcategories have many more pages than the supercategories
and that there is a significant amount of information per page.  In
the case of Wikipedia, there are an average of 25.7 pages per category
\cite{1321474}. The assumption for collecting the training data is the
more subcategory data we have, the more detailed our description of
our category. Considering that there are many categories that have
much more than 26 pages, we instituted a PlusOne mechanism to extract
extra information. This mechanism checks if a subcategory has an
adequate number of pages α to fully describe its subtopic. We set this
number to ten times the average, or 260. $Level$ represents how many
extra levels we are to go down in the hierarchy, if
necessary. SubjectSet is the overall set of all pages associated with
the blanket structure along with any plusOne subjects obtained.

\begin{lstlisting}[language=Python,frame=none,tabsize=2,caption=BlanketSubjectRetreival,label=BlanketSubjectRetreival,basicstyle=\small]
def BlanketSubjectRetreival(blanket, maxLevel):
	for category in blanket:
		subjectSet.add(grabsubjects(category))
		diff = afterSize - beforeSize
		if diff <= a and category is subcategory:
			PlusOneMechanism(category, maxLevel)
	return subjectSet
\end{lstlisting}

\begin{lstlisting}[language=Python,frame=none,tabsize=2,caption=PlusOneMechanism, label=PlusOneMechanism,basicstyle=\small]
def PlusOneMechanism(category, level):
	plusOneSet = grabPlusOneSubcategories(category)
	for subcategory in plusOneSet:
		subject.add(grabSubjects(subcategory))
		diff = afterSize - beforeSize
		if diff <= a and level > 0:
			PlusOneMechanism(subcategory, level-1)

>>>>

\section{Representing and Ontological Realms}
Two types of ontologies are used by our system:
\begin{enumerate}
\item Realm ontologies, comprising a heterarchy of categories that
  characterize terms that can appear in queries.
\item SSQ ontologies, used to describe the form of particular
  realm-specific queries.
\end{enumerate}
For any particular ontological realm, the number of potential
terms and their associated categories can be quite large.
Construction of a realm ontology and the terms associated
with its categories would be an extremely laborious task
for any non-trivial realm. The realm of automobiles (which
we use for illustration in this paper) contains, for example,
over XXXX categories and XXXX terms. We were unable to find
an appropriate ontology for this realm, so we constructed it
using categories from the DBPedia \cite{Auer07dbpedia:a}.
The primary benefit of using the DBPedia for this purpose is
that not only does it supply a categorical heterarchy, but it
also links to Wikipedia documents which provides us with a large
realm-specific document corpus.

\subsection{Category Heterarchy}

To support our process, we map DBPedia categories into classes in our realm ontology with the \textit{superclass/subclass} relationships built using DBPedia properties \textit{broader/narrower}. By using OWL, we can exploit the OWL API for matching SSQ ontologies that reference these realm ontologies.

%Start with a collection of relevant categories

The subcategories of the category Automobiles (… Driving, Traffic Law,
Automobiles by Decade, Auto Racing …) can be seen as grabbing
information specific to the category. The super categories (Road
Vehicles) place the category in a higher perspective, abstractly
describing basketball as a concept. The spousal categories
(...Motor Sport, Individual Sport...) are an abstract description of
the subcategories.

Clustering the categories alone does not guarantee adequate corpus
creation. Since the above model relies on the subcategories to
describe specifics of a given category, the ideal situation would be
that the subcategories have many more pages than the super categories
and that there is a significant amount of information per page.  In
the case of Wikipedia, there are an average of 25.7 pages per category
\cite{1321474}. The assumption for collecting the training data is the
more subcategory data we have, the more detailed our description of
our category. Considering that there are many categories that have
much more than 26 pages, we instituted a PlusOne mechanism to extract
extra information. This mechanism checks if a subcategory has an
adequate number of pages α to fully describe its subtopic. We set this
number to ten times the average, or 260. $Level$ represents how many
extra levels we are to go down in the hierarchy, if
necessary. SubjectSet is the overall set of all pages associated with
the blanket structure along with any plusOne subjects obtained.

\begin{lstlisting}[language=Python, frame=none, tabsize=2, caption=BlanketSubjectRetreival, label=BlanketSubjectRetreival, basicstyle=\small]
def BlanketSubjectRetreival(blanket, maxLevel):
	for category in blanket:
		subjectSet.add(grabsubjects(category))
		diff = afterSize - beforeSize
		if diff <= a and category is subcategory:
			PlusOneMechanism(category, maxLevel)
	return subjectSet
\end{lstlisting}

\begin{lstlisting}[language=Python, frame=none, tabsize=2, caption=PlusOneMechanism, label=PlusOneMechanism, basicstyle=\small]
def PlusOneMechanism(category, level):
	plusOneSet = grabPlusOneSubcategories(category)
	for subcategory in plusOneSet:
		subject.add(grabSubjects(subcategory))
		diff = afterSize - beforeSize
		if diff <= a and level > 0:
			PlusOneMechanism(subcategory, level-1)

@@
